---
title: "Project"
author: "Arvind Chaudhary"
date: "06/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Presentation


### For more information, click on the link below.
URL: *https://www.coursera.org/learn/data-products/peer/tMYrn/course-project-shiny-application-and-reproducible-pitch*

---

## DataSet : mtcars

### Car Road Tests and Motor Trend 

> We borrowed the data from a mazagine published in nineteen seventy four. The data consist of aerodynamic data and engine efficiency for a few cars during that period.
### Source
> Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391-411.
```{r}
library(datasets)
head(mtcars, 3)
```
---
## mtcars Dataset - Format

**A data frame with 32 observations on 11 variables.**

| Index | Field | Detail |
------- | ----- | ------ |
| [1, ] | mpg | Miles/(US) gallon |
| [2,]  | cyl | Number of cylinders |
| [3, ]	| disp | Displacement (cu.in.) |
| [4, ]	| hp | Gross horsepower |
| [5, ]	| drat | Rear axle ratio |
| [6, ]	| wt | Weight (lb/1000) |
| [7, ]	| qsec | 1/4 mile time |
| [8, ]	| vs | V/S |
| [9, ]	| am | Transmission (0 = automatic, 1 = manual) |
| [10,]	| gear | Number of forward gears |
| [11,]	| carb | Number of carburetors |

---

## Code

```r
  formulaTextPoint <- reactive({
    paste("mpg ~", "as.integer(", input$variable, ")")  })
  
  fit <- reactive({
    lm(as.formula(formulaTextPoint()), data=mpgData)  })
  ...
  output$fit <- renderPrint({
    summary(fit()) })
  
  output$mpgPlot <- renderPlot({
    with(mpgData, {
      plot(as.formula(formulaTextPoint()))
      abline(fit(), col=2)
    })  })
```